---
title: "A template for writing manuscripts in Rmarkdown"

author: Thaise Ricardo de Freitas^1^*, Elisabeth Alve^1^, Silvia Hess^1^, Paul Renaud^2,3^

# date: `r Sys.Date()`

output:
  bookdown::word_document2:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    df_print: kable
    keep_md: yes
    number_sections: no
    toc: no
    reference_docx: templates/Word_template.docx
    
csl: templates/ecology.csl
# csl: https://www.zotero.org/styles/ecology
bibliography: references.bib
---

^1^ Department of Geosciences, University of Oslo, PO Box 1047 Blindern, 0316 Oslo, Norway

^2^ Akvaplan-niva, Fram Centre for Climate and the Environment, 9296 Tromsø, Norway

^3^ University Centre on Svalbard, 9171 Longyearbyen, Norway

`*` Corresponding author: [thaiser\@uio.no](mailto:thaiser@uio.no){.email}

# ABSTRACT

Write your abstract here.

*Keywords*: Rmarkdown, reproducible science

```{r setup, include= FALSE, cache=FALSE, message = FALSE}
library("knitr")
library("flextable")
library("readxl")

### Chunk options: see http://yihui.name/knitr/options/ ###
## Text results
opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
# opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "../03_figures/", dpi = 300)

```

# INTRODUCTION

-   Overall importance of Barents Sea in terms of carbon sink and carbon accumulation.

-   What has been documented on carbon accumulation, and carbon sources in the region.

-   "Few studies have paid attention to the origin of the OM in the studied area from the vertical perspective of time" `Não que seja vdd para a regiao, mas é um ponto de partida.`

-   What knowledge gaps about seasonal / bathymetry related changes in sedimentation etc.

-   Our hypothesis / our goal is to investigate environmental pressures on TOC and it's potential sources. And how the pressures may influence storage capacity on these ecosystems in a temporal perspective.

# METHODS

## Study area and sampling

Sediment sampling was performed during three cruises with R/V Kronprins Haakon in 2018 and 2019 (Table 1). Sediment cores with 40 cm length (40x10 cm) were retrieved at nine stations (NPAL04 to NPAL19) with a four-tube multicorer and immediately sliced to 1 cm layers, placed into plastic jars and frozen on board. Twenty-eight cores with 6 cm length (6x5 cm) cores were subsampled from a box corer at six stations (P1 to SICE4) and immediately sliced to 1 cm layers, placed into plastic jars and frozen on board. In the laboratory all samples were freeze-dried under vacuum and homogenized for stable isotopes and organic carbon content analysis.

```{r table-coords}
coord_nansen_print <- read_xlsx("C:/Users/thaiser/OneDrive - Universitetet i Oslo/PhD/maps/dados/coordinates.xlsx", sheet = 4)
set_flextable_defaults(
  font.family = "Arial", 
  font.size = 9,
  font.color = "black",
  table.layout = "fixed",
  digits = 1,
  theme_fun = "theme_booktabs"
  )
ft <- flextable(coord_nansen_print)
ft 
```

## Age determination

We worked in a **beautiful** place with lots of trees, like *Quercus suber* and *Laurus nobilis*.

## Bulk geochemistry analyses

bulk analyses

## Characterization of sedimentary OM

We applied a linear model where

$$
OC_{terr}(\%) = \left(\frac{\delta^{13}Ci - \delta^{13}CM}{\delta^{13}CT - \delta^{13}CM}\right) * 100
$$

```{r model, eval = FALSE}
model <- lm(y ~ x)
```

## Statistical methods

-   Shapiro - Wilk Normality test

-   Kruskal wallis analysis of variance among regions, environmental conditions, sedimentary environments

-   Latitude relationship with parameters with linear regression or other family (glm)

-   Temporal trend (Mann-Kendall, Pettit, Sen slope estimator)

# RESULTS

Trees in forest *A* grew taller than those in forest *B* (mean height: `r mean(25, 31, 28)` versus `r mean(13, 19, 16)` m).

And many more cool results that get updated dynamically, e.g. see Table and Fig. \@ref(fig:scatterplot). Note Tables and Figures are cross-linked and numbered automatically.

```{r Table-Iris}
flextable(head(iris))
```

```{r scatterplot, fig.cap="Just my first figure with a very fantastic caption."}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```

# DISCUSSION

Discuss.

# CONCLUSIONS

Wrap up

# ACKNOWLEDGEMENTS

On the shoulders of giants.

# REFERENCES

::: {#refs}
:::

###### Supplementary Table (on new page)

```{r table-sup}
kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.")
```

###### Supplementary Figure (on new page)

```{r Fig-landscape, fig.cap="A boxplot."}
a <- sort(rnorm(100))
b <- c(rep("Group Small", 35), rep("Group Big", 65))
boxplot(a ~ b)
```

```{r sessioninfo, eval = FALSE}
# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
sessionInfo()
# sessioninfo::session_info()
```
